Sardines only end-to-end atlantisom test

### 2019-06-03 SardinesOnlyatlantisom2SStest.Rmd
comments

#Name of atlantis model output - this is an RData object from the runtruth() function
atlantis_output_name <- "outputCCV3run_truth.RData"

@@

```{r readdata, echo=FALSE}
require(r4ss)
#source("./config/sardine_config.R") this is above for illustration

@@

#Check length compositions match age compositions
ss_length_stdsurv$natlength %>%
  group_by(time,agecl) %>%
  summarise(sum(atoutput))

>>>>

#Name of atlantis model output - this is an RData object from the runtruth() function
#atlantis_output_name <- "outputCCV3run_truth.RData"

@@

```{r readdata}
require(r4ss)
#source("./config/sardine_config.R") this is above for illustration

@@

#Check length compositions match age compositions
#ss_length_stdsurv$natlength %>%
#  group_by(time,agecl) %>%
#  summarise(sum(atoutput))
